Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-11 02_Paper/paper.tex
remove random forests.

\begin{table}
       \centering
       \begin{adjustbox}{width=.45\textwidth}
       \begin{tabular}{ c c c } \toprule
              \textbf{Data of interest} & \textbf{Server Source} & \textbf{Variable}\\ \midrule
              Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
                     Conveyor: Gate \\
                     Conveyor: QC \\
                     Conveyor: Store
                     \end{minipage} \\ \hline
              UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item $xyz$ Gripper position
                     \end{description}
                     \end{minipage} \\ \hline
              Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
                     UR3 gripper open/close \\
                     Grab/drop disk based on disk type
                     \end{minipage} \\ \hline
              Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     OK-NOK label \\
                     $xy$ disk deviation from the center point \\
                     Absolute disk deviation
                     \end{minipage} \\ \hline
              Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     Position \\
                     Speed \\
                     Safe to go
                     \end{minipage} \\ \hline
              Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     Disk Size
                     \end{minipage} \\ \bottomrule
       \end{tabular}
       \end{adjustbox}
       \caption{Industry 4.0 demonstration cell: Relevant data linked with its reference source server.}
       \label{tab:data_source}
\end{table}

\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Use Case        & Description \\ \midrule
              Use Case 1  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Slow \\
                                   Robot position: OK
                            \end{minipage}  \\ \hline
              Use Case 2  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Slow \\
                                   Robot position: NOK
                            \end{minipage}  \\ \hline
              Use Case 3  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Fast \\
                                   Robot position: OK
                            \end{minipage}  \\ \hline
              Use Case 4  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Fast \\
                                   Robot position: NOK
                            \end{minipage}  \\ \hline
              Use Case 5  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Too Fast \\
                                   Robot position: OK
                            \end{minipage}  \\ \hline
              Use Case 6  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Too Fast \\
                                   Robot position: NOK
                            \end{minipage}  \\ \bottomrule
       \end{tabular}
       \caption{Industry 4.0 demostration cell: Controlled Use-Cases.
       Use-Cases with the value \textit{Robot position: NOK} and \textit{Conveyor speed: Too Fast} will result in NOK pieces.}
       \label{tab:use_cases}
\end{table}

>>>>

\begin{table}
       \centering
       \begin{adjustbox}{width=.45\textwidth}
       \begin{tabular}{ c c c } \toprule
              \textbf{Data of interest} & \textbf{Server Source} & \textbf{Variable}\\ \midrule
              Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
                     Conveyor: Gate \\
                     Conveyor: QC \\
                     Conveyor: Store
                     \end{minipage} \vspace{0.1cm} \\ \hline
              UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
                     $xyz$ Gripper position
                     \end{minipage} \vspace{0.1cm} \\ \hline
              Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
                     UR3 gripper open/close \\
                     Grab/drop disk based on disk type
                     \end{minipage} \vspace{0.1cm} \\ \hline
              Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     OK-NOK label \\
                     $xy$ disk deviation from the center point \\
                     Absolute disk deviation
                     \end{minipage} \vspace{0.1cm} \\ \hline
              Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     Position \\
                     Speed \\
                     Safe to go
                     \end{minipage} \vspace{0.1cm} \\ \hline
              Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     Disk Size
                     \end{minipage} \\ \bottomrule
       \end{tabular}
       \end{adjustbox}
       \caption{Industry 4.0 demonstration cell: Relevant data linked with its reference source server.}
       \label{tab:data_source}
\end{table}

\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Use Case        & Description \\ \midrule
              Use Case 1  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Slow \\
                                   Robot position: OK
                            \end{minipage} \vspace{0.1cm}  \\ \hline
              Use Case 2  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Slow \\
                                   Robot position: NOK
                            \end{minipage} \vspace{0.1cm}  \\ \hline
              Use Case 3  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Fast \\
                                   Robot position: OK
                            \end{minipage} \vspace{0.1cm}  \\ \hline
              Use Case 4  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Fast \\
                                   Robot position: NOK
                            \end{minipage} \vspace{0.1cm}  \\ \hline
              Use Case 5  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Too Fast \\
                                   Robot position: OK
                            \end{minipage} \vspace{0.1cm}  \\ \hline
              Use Case 6  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Too Fast \\
                                   Robot position: NOK
                            \end{minipage} \vspace{0.1cm} \\ \bottomrule
       \end{tabular}
       \caption{Industry 4.0 demostration cell: Controlled Use-Cases.
       Use-Cases with the value \textit{Robot position: NOK} and \textit{Conveyor speed: Too Fast} will result in NOK pieces.}
       \label{tab:use_cases}
\end{table}
